---
title: "R Exercises 1 "
author: "Joseph Vargovich"
date: "8/12/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exercise 1
Calculate log(6.2) first using base e and second using base 10.

```{r}
#log(6.2, exp(1)) Default value of log is exp(1), or e for short.  
log(6.2)

#Just use the log10 function instead 
log10(6.2)
```

## Exercise 2
Calculate the square root of 2 and save the result as the variable named sqrt2. Have R display the decimal value of sqrt2. Hint: use Google to find the square root function. Perhaps search on the keywords “R square root function”.

```{r}
sqrt2 <- sqrt(2)
sqrt2
```



## Exercise 3
This exercise walks you through installing a package with all the datasets used in the textbook The Statistical Sleuth.

Install the package Sleuth3 on your computer using RStudio.
Load the package using the library() command.
Print out the dataset case0101
```{r}
#Code to install the Sleuth3 package.
#install.packages("Sleuth3")

#First, load the package.
library(Sleuth3)

#Load readr to export to csv for Python solution
library(readr)

#Print the dataset case0101
data("case0101")
write.csv(case0101, "Slueth.csv", row.names = F)
head(case0101)
```

 
 