---
title: "Module8"
author: "Joe Vargovich"
date: "9/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Exercise 1 - Create vectors of length three and add them. 
```{r}
vec_a = c(2,4,6)
vec_b = c(8,10,12)

vec_c = vec_a + vec_b

vec_c
```

# Exercise 2 - Addition of vectors of differing size
```{r}
vec_d = c(14,20)

#The recycling rule allows us to add two vectors of differing length as we can 
#recycle the values of the shorter one and add them to the longer vector. 
vec_d + vec_a
```
# Exercise 3 - Add a constant to a vector       
```{r}
# Add 5 to the vector a.
vec_a + 5

#This works without error or warning as the one element is applied to each element
# of the target vector. We are not adding vectors here! No warning! 
```
#Exercise 4 - Generate a vector of integers with two methods
```{r}
#1
seq(1,5)

#2
1:5
```

#Exercise 5 - Generate a vector of even integers with two methods
```{r}
#1
seq(2,20,2)

#2
(1:10) * 2
```
# Exercise 6 - Generate a vector of 21 evenly spaced elements between 0 and 1
```{r}
x = seq(0,1, length=21)

x
```
# Exercise 7 - Generate a vector by repeating another one
```{r}
to_repeat = c(2,4,8)

result = rep(to_repeat, 3)

result
```
#Exercise 8 - Generate another vector with rep, with repeats in order using each
```{r}
result = rep(to_repeat, each=4)

result

```

#Exercise 9  - Work with the letters R vector
```{r}
cat(as.character(letters), sep = ",", file = "letters.txt", append = TRUE)
#a. Get the 9th element of letters
letters[9]

#b. Extract the subvector with the 9th, 11th, and 18th elements
letters[c(9,11,18)]

#c. Extract the subvector that is everything but the last two letters
letters[1:24]
```
#Exercise 10 - Create a matrix and perform operations
```{r}
#ai.- Using the matrix function and seq function
matrix1 = matrix(seq(2,30, 2), nrow = 3, ncol = 5, byrow=TRUE)
matrix1

#aii. - Chaining rbinds
row1 = seq(2,10, 2)
row2 = seq(12,20, 2)
row3 = seq(22,30, 2)
matrix2 = rbind(row1,row2) %>%
  rbind(row3)

matrix2

#b. Grab the second row of our matrix
matrix1[2,]

#c. Grab the second element of the third row of our matrix
matrix1[3,2]
```
#Exercise 11 - Create and manipulate a data frame. 
```{r}
#a. Create dataframe my.trees
my.trees = data.frame(
  Girth = c(8.3, 8.6,8.8,10.5, 10.7, 10.8, 11.0),
  Height = c(70, 65, 63, 72, 81, 83, 66),
  Volume = c(10.3, 10.3, 10.2, 16.4, 18.8, 19.7, 15.6)
)

#b. Extract the third observation (row) fron the dataframe
my.trees[3,]

#c. Extract the Girth column by name
my.trees$Girth

#d. Extract all but the fourth row
my.trees[-c(4),]

#e. Use the which command to create a vector on condition
index = which(my.trees$Girth > 10)
index

#f. Create a data set with just the large trees
large.trees = data.frame(
  Girth = my.trees$Girth[index],
  Height = my.trees$Height[index],
  Volume = my.trees$Volume[index]
)
large.trees

#g. Create a data set with just the small trees
small.trees = data.frame(
  Girth = my.trees$Girth[-c(index)],
  Height = my.trees$Height[-c(index)],
  Volume = my.trees$Volume[-c(index)]
)
small.trees
```
#Exercise 12 - Describe the differnece between the two data frame row removal methods
```{r}
df <- data.frame(name= c('Alice','Bob','Charlie','Daniel'),
                 Grade = c(6,8,NA,9))

#This will remove the rows that are na as per the - sign. 
df[ -which(  is.na(df$Grade) ), ]
#This will only select the rows that are not na. The ! operator negates the is.na boolean. 
df[  which( !is.na(df$Grade) ), ]
```

#Exercise 13 - Using expand.grid
```{r}
expand.grid( F1=c('A','B'), F2=c('x','w','z'), replicate=1:2 )


expand.grid( x=seq(-4,4,by=.01), 
             dist=c('Normal','t'), 
             df=c(2,3,4,5,10,15,20,30) ) %>%
  mutate( y = if_else(dist == 't', dt(x, df), dnorm(x) ) ) %>%
  ggplot( aes( x=x, y=y, color=dist) ) + 
  geom_line() + 
  facet_wrap(~df)
```
#Exercise 14 - Create and manipulate a list
```{r}
#a. List creation
x = c(4,5,6,7,8,9,10)
y = c(34,35,41,40,45,47,51)
slope = 2.82
p.value = 0.000131

listStruct = list(X = x, Y=y, Slope=slope, Pval=p.value)
listStruct

#b. Grab the second value of the list (which is y)
listStruct[2]

#c. Grab our p-value
listStruct['Pval']
```
#Exercise 15 - Examine the data structures used with linear models lm()
```{r}
#a. Load the cherry trees dataset
data(trees)

#b. Examine the data frame using str()
str(trees)

#c. Perform a regression relating volume of lumber to the girth and height of the tree
m = lm(Volume ~ Girth + Height, data=trees)

#d. Use the str command to inspect the model m. Extract the coefficients from the list.
str(m)

m['coefficients']
```




