---
title: "Module6"
author: "Joe Vargovich"
date: "9/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Exercise 1 - Work with the political candidate dataset.
```{r}
#Import the data from GH.
prez <- readr::read_csv('https://raw.githubusercontent.com/dereksonderegger/444/master/data-raw/Prez_Candidate_Birthdays')

#a. Re-code the Gender column to have Male and Female levels. 
  #Similarly convert the party variable to be Democratic or Republican.
prez = prez %>% 
  mutate(Party = ifelse(Party == "D", "Democrat", "Republican" ))
head(prez)
#b. Change Bernie Sanders to "Independent"
# Select the row where the candidate is Bernie Sanders 
# and set just his party to Independent. 
prez$Party[prez$Candidate == "Bernie Sanders"] = "Independent"
tail(prez)
```
# Exercise 2 - Density function of X and conditionals for valid values of x. 

### Sample code for built in density function
```{r}
a <- 4      # The min and max values we will use for this example
b <- 10     # Could be anything, but we need to pick something

x <- runif(n=1, 0,10)  # one random value between 0 and 10 

# what is value of f(x) at the randomly selected x value?  
dunif(x, a, b)
```
### a. We need a <= x <= b to return 1/b-a, otherwise return 0.
```{r}

a <- 4
b <- 10
x <- runif(n=1, 0,10)  # one random value between 0 and 10 

if( x < a ){
  result <- 0
}else if( x <= b ){
  result <- 1/(b-a) #Parenthesis are important here! Order of ops.
}else{
  result <- 0
}

print(paste('x=',round(x,digits=3), '  result=', round(result,digits=3)))

```
### b. Create conditionals with the "and" and the "or" operators to calculate the density function properly.
```{r}
#i. 
x <- runif(n=1, 0,10)  # one random value between 0 and 10 
if( (a<=x) & (x<=b) ){ # AND (&) is necessary here as both bounds apply
  result <- 1/(b-a)
}else{
  result <- 0
}
print(paste('x=',round(x,digits=3), '  result=', round(result,digits=3)))

#ii.
x <- runif(n=1, 0,10)  # one random value between 0 and 10 
if( (x<a) | (b<x) ){ # OR (|) is needed here as either condition would break 
  result <- 0         # the bounds of the density function
}else{
  result <- 1/(b-a)
}
print(paste('x=',round(x,digits=3), '  result=', round(result,digits=3)))

#iii.
x <- runif(n=1, 0,10)  # one random value between 0 and 10 
result <- ifelse( a<x & x<b, 1/(b-a), 0 )
print(paste('x=',round(x,digits=3), '  result=', round(result,digits=3)))

```
# Exercise 3 - For loops to create multiple graphs concisely

### Example code for the desired graph
```{r}
df <- 4
N <- 1000
x <- seq(-4, 4, length=N)

data <- data.frame( 
  x = c(x,x),
  y = c(dnorm(x), dt(x, df)),
  type = c( rep('Normal',N), rep('T',N) ) )

write.csv(data, "degreeFreedomGraph.csv")

# make a nice graph
myplot <- ggplot(data, aes(x=x, y=y, color=type, linetype=type)) +
  geom_line() +
  labs(title = paste('Std Normal vs t with', df, 'degrees of freedom'))

# actually print the nice graph we made
print(myplot) 
```

### a. Use a for loop to create similar graphs for degrees of freedom 2,3,4 ..., 29,30
```{r}
df = 4
# make a nice graph
  data <- data.frame( 
  x = c(x,x),
  y = c(dnorm(x), dt(x, df)),
  type = c( rep('Normal',N), rep('T',N) ) )


for(df in 2:30){
  #Update our y column for each df value
  data$y <- c(dnorm(x), dt(x, df))
  
  #Create a new plot for each new y column
  myplot <- ggplot(data, aes(x=x, y=y, color=type, linetype=type)) +
    geom_line() +
    labs(title = paste('Std Normal vs t with', df, 'degrees of freedom'))
  
  print(myplot)
}
```

### b. Use a for loop to create similar graphs for degrees of freedom 2,3,4,5,10,15,20 25,30
```{r}
dfVec = c(2,3,4,5,10,15,20,25,30)
for(df in dfVec){
  # Update our y column for each df value
  data$y <- c(dnorm(x), dt(x, df))
  
  # Make a graph to reflect each new df value  
  myplot <- ggplot(data, aes(x=x, y=y, color=type, linetype=type)) +
    geom_line() +
    labs(title = paste('Std Normal vs t with', df, 'degrees of freedom'))
  
  print(myplot)
}
```





















